Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-23 tex/main/manuscript.tex
整理完全部讨论

% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，灵活性进一步降低，
However, in the regional cycle regime of water utilization, basins still face new structural traps and require further transformation. Firstly, in line with paradox of irrigation efficiency \cite{graftonParadoxIrrigationEfficiency2018}, significant improvement in agricultural irrigation efficiency (or decline in water use intensity) has been accompanied by a resurgence in irrigated area, 
resulting in an unabated and weak upward trend in water stress.
% 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
As integrated basin allocation dominates water allocation, the propensity to allocate water between non-supply industries, such as industrial services, and agriculture is becoming fixed. At the same time, the flexibility of water use is declining since domestic water use and thermal water use growth rapidly. Typically, similar to other cases, these may lead to a reduction in watershed resilience and leave highly coupled human-water systems facing greater vulnerability to collapse --a typically structural trap.
% 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
% 总结：整个流域需进一步转型与适应，以实现高质量发展。
Therefore, based on the identification of the current basin transition stage and development dilemma, 
further transitional governance is still needed to achieve high-quality sustainable development of the basin.

>>>>

% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，倾向性停滞，灵活性进一步降低，）
However, in the regional cycle regime of water utilization, the Yellow River Basins still faces structural traps and require further transformation according to changes within the human-water system. 
Firstly, in line with paradox of irrigation efficiency, significant improvement in agricultural irrigation efficiency (i.e. decline in water use intensity) has been accompanied by a resurgence in irrigated area, resulting in an unabated and weak upward trend in water stress \cite{graftonParadoxIrrigationEfficiency2018}.
% 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
Secondly, the changing tendentiousness between non-provisioning (i.e. industry and urban services) and provisioning (i.e. domestic and irrigation water use) is stagnating (see Figure~\ref{fig:dimensions}E) because of rigidify in the industrial structure. 
At the same time, the flexibility of water use is declining since domestic water use and thermal water use growth rapidly (supplementary Fig. S4). 
% 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
% 总结：整个流域需进一步转型与适应，以实现高质量发展。
Typically, these may lead to a reduction in resilience of basins and leave highly coupled human-water systems facing greater vulnerability to collapse --as a structural trap \cite{cummingResilienceBigRiver2011}. Therefore, based on the identification of current phases and development traps by the transition framework, further transformative governance is still needed to achieve a high-quality sustainable development of the basin \cite{scoonesTransformationsSustainabilityCombining2020a}.
